Adversarial Deep Neural Networks Effectively Remove Nonlinear Batch Effects from Gene-Expression Data

### 2019-05-30 thesis.tex
Add acknowledgments

\begin{titlingpage}
	\setcounter{page}{3}
	\phantomsection
	\addcontentsline{toc}{section}{Acknowledgments}
	\begin{center}
		ACKNOWLEDGMENTS\\
		TODO: Fill this out.
	\end{center}
\end{titlingpage}

>>>>

\begin{titlingpage}
	\setcounter{page}{3}
	\phantomsection
	\addcontentsline{toc}{section}{Acknowledgments}
	\begin{center}
		ACKNOWLEDGMENTS
	\end{center}
	\paragraph{}
	Thanks to Dr. Stephen Piccolo, whose mentorship over the past four years has shaped my education much more than the classes I took.
	Thanks to Dr. Mark Clement and Dr. David Wingate for participating in my graduate committee and providing helpful feedback throughout my degree.
	Thanks to my office- and lab-mates, who let me bounce ideas off of them.
	Thanks to the BYU Department of Biology for funding my education, and specifically to Dr. Byron Adams for making the graduate experience more enjoyable, and to Gentri Glaittli for helping me to navigate the university requirements.
	Thanks to my grandmother, Jennette Hawkes, whose financial help came at a critical time in my education.
	Thanks to my parents, Minnie and Bryan Dayton, for teaching me the value of an education, and to my sisters Merinda, Louisa, Eliza, and Anna for their support.
	Thanks to Dr. Paul Horton, whose thorough peer review provided me with the idea for this project.
	Thanks to the researchers who generated the data for this project and who made it available.

	Most of all, thanks to my wife, Zanna, for her love and support over the course of my graduate education.
\end{titlingpage}
